---
title: "FRDS Global Flagship Report 2025"
subtitle: "Red Cross Red Crescent National Society Indicators"
author: "International Federation of Red Cross and Red Crescent Societies"
date: "2025"
format:
  closeread-html:
    # Closeread extension: quarto add quarto-ext/closeread
    cr-style:
      narrative-col-width: "minmax(260px, 480px)"
      sticky-col-width: "1fr"
      narrative-background-color: "#ffffff"
      section-background-color: "#011E41"
    embed-resources: true
    toc: false
    theme:
      - cosmo
      - ifrc-theme.scss
execute:
  echo: false
  warning: false
---

```{r setup}
#| include: false
library(tidyverse)
library(ggplot2)

# Dummy FRDS data
volunteers <- tibble(
  region    = c("Asia Pacific", "Americas", "Africa", "Europe", "MENA"),
  millions  = c(6.8, 4.1, 3.2, 2.1, 1.3),
  color     = c("#EE334E", "#F0A400", "#0096D6", "#43A047", "#B85ED4")
)

reach <- tibble(
  programme = c("Disaster Relief", "Health", "Livelihoods", "Migration", "Other"),
  share     = c(42, 28, 15, 10, 5),
  color     = c("#EE334E", "#0096D6", "#43A047", "#F0A400", "#9E9E9E")
)

operations <- tibble(
  year    = 2020:2024,
  total   = c(145, 138, 162, 178, 156),
  climate = c(75, 74, 98, 114, 105)
)

# IFRC theme for ggplot
theme_ifrc <- function() {
  theme_minimal(base_family = "Open Sans") +
  theme(
    plot.background    = element_rect(fill = "#011E41", colour = NA),
    panel.background   = element_rect(fill = "#011E41", colour = NA),
    panel.grid.major   = element_line(colour = "rgba(255,255,255,0.08)"),
    panel.grid.minor   = element_blank(),
    axis.text          = element_text(colour = "rgba(255,255,255,0.55)", size = 11),
    axis.title         = element_blank(),
    plot.title         = element_text(colour = "white",  family = "Montserrat",
                                      face = "bold", size = 14),
    plot.subtitle      = element_text(colour = "rgba(255,255,255,0.6)", size = 11),
    legend.background  = element_rect(fill = "#011E41", colour = NA),
    legend.text        = element_text(colour = "rgba(255,255,255,0.7)", size = 10),
    legend.title       = element_blank()
  )
}
```

<!-- ═══════════════════════════════════════════════════
     Closeread scrollytelling sections
     Each :::{.cr-section} creates a two-column layout:
       • Sticky element (#cr-id) anchors to the right
       • Narrative text scrolls on the left
       • @cr-id in text triggers focus transitions
════════════════════════════════════════════════════ -->

## The World's Largest Humanitarian Network {.hero-title}

*FRDS — the Financial Reporting and Data System — captures annual performance data
from all 191 Red Cross Red Crescent National Societies.*

---

:::{.cr-section}

The IFRC's FRDS tracks data from every corner of the globe. @cr-map

191 National Societies operate in 191 countries and territories — meaning almost no
place on earth lacks a local Red Cross or Red Crescent presence.

In 2024, **176 National Societies** submitted complete FRDS returns, a record
reporting rate of 92%. @cr-map

:::{#cr-map}
```{r}
#| fig-width: 8
#| fig-height: 4.5
# In production: use {rnaturalearth} + ggplot2 geom_sf
# Placeholder: world map with country counts
world_map <- rnaturalearth::ne_countries(scale = "medium", returnclass = "sf")

ggplot(world_map) +
  geom_sf(fill = "rgba(255,255,255,0.1)", colour = "rgba(255,255,255,0.22)",
          linewidth = 0.2) +
  coord_sf(crs = "+proj=natearth") +
  labs(title = "191 National Societies", subtitle = "countries and territories · 2024") +
  theme_ifrc() +
  theme(axis.text = element_blank(), panel.grid = element_blank())
```
:::

:::

---

:::{.cr-section}

At the heart of the network are volunteers. @cr-bar

In 2024, over **17.5 million volunteers** gave their time and skills — more than
any other humanitarian organisation in the world.

The Asia Pacific region contributes the largest share. Volunteer numbers have grown
**+12%** since 2020, reversing pandemic-era declines. @cr-bar

:::{#cr-bar}
```{r}
#| fig-width: 7
#| fig-height: 4
ggplot(volunteers, aes(x = millions, y = fct_reorder(region, millions), fill = color)) +
  geom_col(width = 0.65, show.legend = FALSE) +
  geom_text(aes(label = paste0(millions, "M")), hjust = -0.2,
            colour = "rgba(255,255,255,0.65)", family = "Montserrat",
            fontface = "bold", size = 3.8) +
  scale_fill_identity() +
  scale_x_continuous(expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Volunteers by Region · 2024") +
  theme_ifrc()
```
:::

:::

---

:::{.cr-section}

Across all programmes, National Societies reached **1.9 billion people** in 2024.
@cr-donut

Disaster relief and emergency health remain the largest programme areas by numbers
served, but health and livelihoods are growing fastest. @cr-donut

MENA National Societies saw a **+34% rise** in people reached, driven by responses
in Gaza and Sudan. @cr-donut

:::{#cr-donut}
```{r}
#| fig-width: 6
#| fig-height: 4.5
ggplot(reach, aes(x = 2, y = share, fill = color)) +
  geom_col(width = 1, colour = "#011E41", linewidth = 0.8, show.legend = FALSE) +
  geom_text(aes(label = paste0(programme, "\n", share, "%")),
            position = position_stack(vjust = 0.5),
            colour = "white", family = "Open Sans", size = 3.2, lineheight = 1.2) +
  scale_fill_identity() +
  coord_polar(theta = "y", start = 0) +
  xlim(0.5, 2.5) +
  labs(title = "People Reached by Programme · 2024") +
  theme_ifrc() +
  theme(axis.text = element_blank(), panel.grid = element_blank())
```
:::

:::

---

:::{.cr-section}

National Societies launched **156 major emergency operations** in 2024. @cr-line

Climate-related events now account for **67% of all operations**, up from 52% in 2020.
The average operation now lasts 8.3 months — up from 5.1 months in 2019. @cr-line

:::{#cr-line}
```{r}
#| fig-width: 7
#| fig-height: 4
operations_long <- operations |>
  pivot_longer(c(total, climate), names_to = "type", values_to = "n") |>
  mutate(type = recode(type, total = "All operations", climate = "Climate-related"))

ggplot(operations_long, aes(x = year, y = n, colour = type)) +
  geom_area(data = filter(operations_long, type == "Climate-related"),
            aes(fill = type), alpha = 0.18, show.legend = FALSE) +
  geom_line(linewidth = 2, show.legend = TRUE) +
  geom_point(size = 4) +
  scale_colour_manual(values = c("All operations" = "white",
                                 "Climate-related" = "#EE334E")) +
  scale_fill_manual(values = c("Climate-related" = "#EE334E")) +
  scale_x_continuous(breaks = 2020:2024) +
  scale_y_continuous(limits = c(0, 210)) +
  labs(title = "Major Emergency Operations · 2020–2024") +
  theme_ifrc() +
  theme(legend.position = "bottom")
```
:::

:::
